---
title: "Example Dataset in `SampleCore`"
author: "J. Aravind"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: united
    highlight: textmate
    toc: TRUE
link-citations: yes
csl: frontiers.csl
bibliography: REFERENCES.bib
vignette: |
  %\VignetteIndexEntry{Introduction}
  %\usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown_notangle}
---

```{r, echo=FALSE}
# out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
out_type <- "html"
```

```{r, results='asis', echo=FALSE}
switch(out_type,
    html = {cat("<p> ICAR-National Bureau of Plant Genetic Resources, New Delhi.</p>")},
    latex = cat("\\begin{center}
 ICAR-National Bureau of Plant Genetic Resources, New Delhi.

\\end{center}" )
)
```

\begin{center}
\vspace{6pt}
\hrule
\end{center}

\tableofcontents

# Introduction

The example datasets `cassava_EC` and `cassava_CC` in `EvaluateCore` for demonstrating various functions were generated using the following steps from the source data [@international_institute_of_tropical_agriculture_cassava_2019]. 

# Setup the environment

```{r}
# Load required packages
library(EvaluateCore)
library(cluster)
library(NbClust)
```

# Load and prepare data

```{r}
# Get data from EvaluateCore

data("cassava_EC", package = "EvaluateCore")
data = cbind(Genotypes = rownames(cassava_EC), cassava_EC)
quant <- c("NMSR", "TTRN", "TFWSR", "TTRW", "TFWSS", "TTSW", "TTPW", "AVPW",
           "ARSR", "SRDM")
qual <- c("CUAL", "LNGS", "PTLC", "DSTA", "LFRT", "LBTEF", "CBTR", "NMLB",
          "ANGB", "CUAL9M", "LVC9M", "TNPR9M", "PL9M", "STRP", "STRC",
          "PSTR")
rownames(data) <- NULL

# Convert qualitative data columns to factor
data[, qual] <- lapply(data[, qual], as.factor)

# Standardise quantitative data column
data[, quant] <- lapply(data[, quant], function(x) {
  scale(x)[, 1]
})
```

# Perform the clustering

```{r}
# Set the seed
set.seed(123)

# Get the Gower's distance matrix
data_dist <- daisy(x = data[, c(qual, quant)], metric = "gower")

# Perform Ward's minimum variance clustering
data_clust <- hclust(d = data_dist, method = "ward.D2")

# Identify optimum number of cluster
nc_result <- NbClust(diss = data_dist, distance = NULL, 
                     min.nc = 2, max.nc = 6,
                     method = "ward.D2",
                     index = "cindex")
nc <- nc_result$Best.nc["Number_clusters"]

# Plot dendrogram with nc = 6 clusters
plot(as.dendrogram(data_clust))
rect.hclust(data_clust, k = nc)

# Add the group to the original data
cassava_EC_gp <- cassava_EC
cassava_EC_gp$Cluster <- as.roman(nc_result$Best.partition)
cassava_EC_gp$Cluster <- as.factor(as.character(cassava_EC_gp$Cluster))

# View the final data
str(cassava_EC_gp)
head(cassava_EC_gp)
```

# Export the dataset

```{r, eval=FALSE, echo=TRUE}

write.csv(cassava_EC_gp, "cassava_EC_gp.csv", row.names = TRUE)

```

# Session Info

```{r}
sessionInfo()
```

# References
